---
title: "Priming the distributive/cumulative contrast"
author: "Yizhen Jiang"
date: '2022-07-16'
output: 
  html_document:
    number_sections: yes
    theme: cerulean
    highlight: kate
    toc: yes
    toc_float:
      collapsed: true
      smooth_scroll: true
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# Load R scripts
knitr::read_chunk("demographics.R")
knitr::read_chunk("priming task.R")

# Load packages
library(broom)        # for tidy model outputs
library(kableExtra)   
library(gt)           
library(gtsummary)    # for nice tables
library(plotly)       # for nice graphs
```

# Introduction

This document is used to report the results of the data analyses ("demographics.R" and "priming task.R"). Currently, it contains most of the results reported in the essay. It's still under construction (7/16/2022).

# Demographics

## Data summary

```{r demographics, echo=TRUE, message=TRUE, warning=TRUE}

```

```{r demographics summary, echo=TRUE, message=TRUE, warning=TRUE}
demographics.summary %>% 
  round(digits = 1) %>% 
  kbl() %>% 
  kable_paper("hover", full_width = F)
```

# Priming task

## Data treatment & processing

```{r load packages, echo=TRUE, message=TRUE, warning=TRUE}

```

```{r data processing, message=TRUE, warning=TRUE}

```

## Data summary

# Average completeion time
Average completion time is `r mean(completiontime$compeletion.time)`

# Mean accuarcy rates of primes and fillers
Mean accuracy rate of primes
```{r}

```
Mean accuracy rates of prime trials by Condition (Distributive, Cumulative, Control)
```{r}
t1
```
Mean accuracy rate of fillers
```{r}

```

Mean accuracy rates of fillers by Condition (Distributive, Cumulative, Baseline)
```{r}
t2
```




## Data visualization

```{r}
ggplotly()
```

## Data analysis

```{r}
modelsummary %>%  
  tidy() %>% 
  kbl() %>% 
  kable_paper("hover", full_width = F)

modelsummary %>%  
  glance() %>% 
  kbl() %>% 
  kable_paper("hover", full_width = F)
```

# Session info

`r R.version.string` `lme4` (v. `r packageVersion("lme4")`)

```{r session info, message=FALSE}
sessionInfo()
```
